---
title: "Ecosystem"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval=FALSE)
```

### Github

```
ecosystem_case-master
      |___Data
          |__BioChemDesc.csv
          |__Habitatattributes.csv
          |__PhysDesc.csv
          |__ROMS.csv
          |__Zoo.csv
          |__copernicus_bio_monthly.RData
          |__copernicus_phys_monthly.RData
          |__gebco_2020.RData
          |__mean_wave_direction.RData
          |__mean_wave_period.RData
          |__sea_bottom_salinity.RData
          |__sea_bottom_temperature.RData
          |__sea_surface_salinity.RData
          |__sea_surface_temperature.RData
          |__sea_surface_x_velocity.RData
          |__sea_surface_y_velocity.RData
          |__significant_wave_height.RData
          |__Zoo.RData
          |__ke_currents.RData
          |__ke_waves.RData
          
      |___functions
          |__combine.R 
          |__ocean_variables.R
     
      |___results
          |___data
             |__aggregated
             |__spatial
          |___plots
          |___Template.Rproj
          |__Convert_to_rmd.html
      |__temp
         |__a_temp.R
      |__WWW
        |__diag_new.png
        |__Niamh.png
      |__app_toolbox.R
      |__report.Rmd
      |__Sources.html
      |__Sources.rmd
      |__ecosystem_case.Rproj
       
    
```




## __Data__ 
### .csv (No updates needed)

All files used by app_toolbox.R,report.Rmd,Sources.Rmd.

_PhysDesc.csv_

_BioChemDesc.csv_

_ROMS.csv_

_Zoo.csv_

_Habitatattributes.csv_



All data files saved as .RData to reduce file size (github commit allows only under 100mb)

### sb2019.RData
Seabed Habitat shapefile provided by INFOMAR as shapefile which was opened in Rstudio and saved as .RData


### gebco_2020.RData
2D netCDF grid downloaded from https://download.gebco.net/ using boundaries Lon: from 56 till 48, Lat: from -18 till -2.
Save file as gebco_2020.nc and use following script to create gebco_2020.RData

```{r}
library(raster)
gebco_2020<-raster("gebco_2020.nc")
gebco_2020<- readAll(gebco_2020) # force data into memory
save(gebco_2020,file="Data/gebco_2020.RData")

```

### copernicus_bio_monthly.RData

netCDF grid downloaded from https://resources.marine.copernicus.eu/?option=com_csw&view=details&product_id=IBI_REANALYSIS_BIO_005_003 using boundaries Lon: from 56 till 48, Lat: from -18 till -2.

Save file as copernicus_bio_monthly.nc and use following script to create copernicus_bio_monthly.RData
```{r}
library(raster)

####Copernicus Bio
rm(list=ls())
vv<-read.csv("Data/BioChemDesc.csv")
for(i in 1:length(vv[[1]])){
  r<-brick("copernicus_bio_monthly.nc" ,varname=as.character(vv[i,1]))
  r<- readAll(r)
  assign(as.character(vv[i,1]),r)}
rm(vv)
rm(i)
rm(r)
save(list=ls(),file = "Data/copernicus_bio_monthly.RData")

```
### copernicus_phys_monthly.RData

netCDF grid downloaded from https://resources.marine.copernicus.eu/?option=com_csw&view=details&product_id=GLOBAL_REANALYSIS_PHY_001_030 using boundaries Lon: from 56 till 48, Lat: from -18 till -2.

Save file as copernicus_bio_monthly.nc and use following script to create copernicus_phys_monthly.RData
```{r}
library(raster)

####Copernicus Physics
rm(list=ls())
vv<-read.csv("Data/PhysDesc.csv")
for(i in 1:length(vv[[1]])){
  r<-brick("copernicus_phys_monthly.nc" ,varname=as.character(vv[i,1]))
  r<- readAll(r)
  assign(as.character(vv[i,1]),r)}
rm(vv)
rm(i)
rm(r)
save(list=ls(),file = "Data/copernicus_phys_monthly.RData")

```
### ROMS

.nc NetCDF3 downloaded from https://erddap.marine.ie/erddap/griddap/IMI_Model_Stats.html using boundaries Lon: from 56 till 48, Lat: from -18 till -2.

Save file as ROMS.nc and use following script to create sea_surface_temperature.RData,
sea_bottom_temperature.RData,
sea_surface_salinity.RData,
sea_bottom_salinity.Rdata,
sea_surface_x_velocity.Rdata,
sea_surface_y_velocity.Rdata,
significant_wave_height.RData,
mean_wave_direction.RData,
mean_wave_period.RData

```{r}
####SPLIT ROMS.nc and SAVE EACH PARAMETER AS .GRD
rm(list=ls())
vv<-read.csv("Data/ROMS.csv")
for(i in 1:length(vv[[1]])){
  r<-brick("ROMS.nc" ,varname=as.character(vv[i,1]))
  r<- readAll(r)
  writeRaster(r, filename=paste0("ROMS/",vv[i,1],".grd"), bandorder='BIL', overwrite=TRUE)
}

# save each grid as .RData
rm(list=ls())
for(i in 1 :9){
  vv<-read.csv("Data/ROMS.csv")
  r<-brick(paste0("ROMS/",vv[i,1],".grd"))
  r<- readAll(r)
  assign(as.character(vv[i,1]),r)
  rm(list=setdiff(ls(), as.character(vv[i,1])))
  save(list=ls(),file=paste0("Data/",ls(),".RData"))
 
}

```
### Zoo.RData

No updates needed..historical data


### ke_currents.RData

Download data file from https://www.emodnet-seabedhabitats.eu/access-data/download-data/?linkid=ke_currents_atlantic.
Unzipp file, rename folder to ke_currents and use following script to create ke_currents.RData

```{r}
library(raster)
ke_currents<-raster("ke_currents/ke_currents_atlantic.tiff")
ke_currents<- readAll(ke_currents) # force data into memory
save(ke_currents,file="Data/ke_currents.RData")

```


### ke_waves.RData

Download data file from https://www.emodnet-seabedhabitats.eu/access-data/download-data/?linkid=ke_waves_atlantic.
Unzipp file, rename folder to ke_waves and use following script to create ke_waves.RData

```{r}
library(raster)
ke_waves<-raster("ke_waves/ke_currents_atlantic.tiff")
ke_waves<- readAll(ke_waves) # force data into memory
save(ke_waves,file="Data/ke_waves.RData")

```

## __functions__

Combine.R(used by app report.Rmd))
ocean_variable.R(data manipulation function used by app and report.Rmd)


## __results__

Empty folder used by app_toollbox.R saving data and plots outputs

## __temp__

 Results temp location while app running at each stage. Content of the folder cleared after last step.

## __www__

diag_new.png image in github page

Niamh.phg  app logo

## __app_toolbox.R__
shiny app

## __Sorces.html__

 Data description tab in app_toolbox.R
## __Sorces.rmd__ 

Used to render Source.html
 
## __ecosystem_case.Rproj__

R project

## __report.Rmd__

Parametarized r-markdown used to generate report in app_toolbox.R
